Goes Here

### 2012-07-30 paper.tex
figures

TexturedShape shape("filename"), goal("filename1");

@@

Deformation
\begin{verbatim}
scene.addForce(new Force(pos, dir, shapeID));
scene.addConstraint(
  new Constraint(FIX_VERTEX, vertexList, shapeID));
Shape goal;
manager.setSimulator(new FEMSimulator());
\end{verbatim}
\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
\subsection{Textured Model}
Input: a textured 3D model and
	measured Albedo of print material.

>>>>

TexturedShape shape("filename");
TexturedShape goal("filename1");

@@

Deformation
\begin{verbatim}
scene.addForce(new Force(pos, dir, shapeID));
scene.addConstraint(
  new Constraint(
    FIX_VERTEX, vertexList, shapeID));
Shape goal;
manager.setSimulator(new FEMSimulator());
\end{verbatim}

\section{Experiments}
\subsection{Previous Work}
Subsurface scattering. Mechanical properties
\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
% 	\includegraphics[width=\textwidth]{a}
   	\caption{}
    \label{fig:ssOrigin}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
%  	\includegraphics[width=\textwidth]{a}
    \caption{}
    \label{fig:ssPrint}
\end{subfigure}
\caption{Subsurface Scattering. (a)Original object. (b)Printed model.}
\label{fig:SS}
\end{figure}

\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
% 	\includegraphics[width=\textwidth]{a}
   	\caption{}
    \label{fig:deformPhoto}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
%  	\includegraphics[width=\textwidth]{a}
    \caption{}
    \label{fig:deformPrint}
\end{subfigure}
\caption{Matching deformation. (a)photo of a slab being pushed. (b)Printed model being pushed.}
\label{fig:deform}
\end{figure}

Two error plots showing subsurface scattering and deformation errors decrease
after each iteration in Figure~\ref{fig:err}.

\begin{figure}
\begin{subfigure}[b]{0.3\textwidth}
	\centering
% 	\includegraphics[width=\textwidth]{a}
   	\caption{}
    \label{fig:ssErr}
    \end{subfigure}
    ~ 
    \begin{subfigure}[b]{0.3\textwidth}
    \centering
%  	\includegraphics[width=\textwidth]{a}
    \caption{}
    \label{fig:deformErr}
\end{subfigure}
\caption{Error plots for 
optimizing subsurface-scattering and deformation properties 
iteratively. (a)Subsurface scattering errors. (b)Deformation errors.}
\label{fig:err}
\end{figure}

\subsection{Textured Model}
Input: a textured 3D model and
	measured Albedo of print material.
